Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-05-29 WSSSPE2_report/WSSSPE2_review.tex
Minor changes - mostly checking to ensure I can push to github.

\newcommand{\todo}[1]{{\color{blue}$\blacksquare$~\textsf{[TODO: #1]}}}
\newcommand{\note}[1]{ {\textcolor{blueish}    { ***Note:      #1 }}}
\newcommand{\katznote}[1]{ {\textcolor{magenta}    { ***Dan:      #1 }}}
\newcommand{\gabnote}[1]{ {\textcolor{cyan}    { ***Gabrielle:     #1 }}}
\newcommand{\nchnote}[1]{  {\textcolor{orange}      { ***Neil: #1 }}}
\newcommand{\manishnote}[1]{  {\textcolor{violet}     { ***Manish: #1 }}}
\newcommand{\davidnote}[1]{  {\textcolor{darkgreen}      { ***David: #1 }}}
\newcommand{\colinnote}[1]{ {\textcolor{red}    {***Colin: #1 }}}
\newcommand{\choinote}[1]{ {\textcolor{orange}    {***Choi: #1 }}}

@@

Testing for infrastructure is easier than testing for models. \katznote{to delete? - don't see how it fits}

@@

Distinction between 100 lines of input files vs. 100 lines of source code \katznote{to delete? - don't see how it fits}

@@

See the ``13 dwarves'' from Berkeley http://www.eecs.berkeley.edu/Pubs/TechRpts/2006/EECS-2006-183.html \katznote{to delete? - don't see how it fits}

>>>>

\newcommand{\todo}[1]{{\color{blue}$\blacksquare$~\textsf{[TODO: #1]}}}
\newcommand{\note}[1]{ {\textcolor{blueish}    { ***Note:      #1 }}}
\newcommand{\katznote}[1]{ {\textcolor{magenta}    { ***Dan:      #1 }}}
\newcommand{\clunenote}[1]{ {\textcolor{orange}    { ***Tom:      #1 }}}
\newcommand{\gabnote}[1]{ {\textcolor{cyan}    { ***Gabrielle:     #1 }}}
\newcommand{\nchnote}[1]{  {\textcolor{orange}      { ***Neil: #1 }}}
\newcommand{\manishnote}[1]{  {\textcolor{violet}     { ***Manish: #1 }}}
\newcommand{\davidnote}[1]{  {\textcolor{darkgreen}      { ***David: #1 }}}
\newcommand{\colinnote}[1]{ {\textcolor{red}    {***Colin: #1 }}}
\newcommand{\choinote}[1]{ {\textcolor{orange}    {***Choi: #1 }}}

@@

Testing for infrastructure is easier than testing for models. \katznote{to delete? - don't see how it fits}
\clunenote{Do not know if I can answer whether it fits, but can expand upon the intent of the sentence.  The idea was to ground people's expectations.   All software can be tested.  But some types of software are much easier to test.  In particular numerical argorithms introduce new issues that increase the difficulty and can represent a high barrier for starting to unit test.   The issues that arise are (1) dealing with numerical error (and in particular roundoff error that accumulates through multiple operations and/or loop iterations, and (2)  the \emph{apparent} lack of oracles for nontrivial cases.)

@@

Distinction between 100 lines of input files vs. 100 lines of source code \katznote{to delete? - don't see how it fits}
\clunenote{I no longer recall the context for this statement.}

@@

See the ``13 dwarves'' from Berkeley http://www.eecs.berkeley.edu/Pubs/TechRpts/2006/EECS-2006-183.html \katznote{to delete? - don't see how it fits}
\clunenote{No opinion - someone thought it was a useful reference for the topic.}
